Recruiting Chapter

### 2020-11-03 manuscript.Rmd
added number of visits to private high schools (total, in-st, out-st) to ego tables

```{r, ego-table-privu, echo = FALSE}
df <- readRDS('./assets/tables/table_ego.RDS')
knitr::kable(
  df %>% select(-Characteristics), row.names = F, # select(-ID, -Characteristics)
  caption = 'ego table caption') %>% landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r, include = FALSE, eval = FALSE}
df <- readRDS('./assets/tables/table_ego.RDS')
#df %>% select(ID,University,Cluster,Type,Rank,c1_lt10,c2_10to25,c3_25to50,`c4_50+`) %>%mutate(lt25 = as.numeric(c1_lt10) + as.numeric(c2_10to25))

@@

```{r, hs-print-privu, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode.RDS') %>% head(n=20)

knitr::kable(
  df %>% select(-school_id,-closeness), caption = 'ego table 3') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r, hs-table-privu-agg, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_agg.RDS')

knitr::kable(df, caption = 'ego table caption') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

@@

```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "caption of 2 mode graph"}
knitr::include_graphics('assets/figures/plot_g_2mode_privu.pdf')
```

@@

```{r emory-region, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "Ego network of Emory University, with geographic region"}
knitr::include_graphics('assets/figures/emory_region.pdf')
```

```{r rank-cluster1, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "Academic rating of private high schools visited by selected colleges from cluster 1"}
knitr::include_graphics('assets/figures/rank_cluster1.pdf')
```

```{r race-cluster4, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "Racial composition of visited private high schools, selected colleges"}
knitr::include_graphics('assets/figures/race_cluster4.pdf')
```

>>>>

<!-- private col/univ -->

```{r, ego-table-privu, echo = FALSE}
df <- readRDS('./assets/tables/table_ego_privu.RDS')
knitr::kable(
  df %>% select(-ID,-Characteristics), row.names = F, # select(-ID, -Characteristics)
  caption = 'ego table private colleges and universities') %>% landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r, include = FALSE, eval = FALSE}
df <- readRDS('./assets/tables/table_ego_privu.RDS')
#df %>% select(ID,University,Cluster,Type,Rank,c1_lt10,c2_10to25,c3_25to50,`c4_50+`) %>%mutate(lt25 = as.numeric(c1_lt10) + as.numeric(c2_10to25))

@@

```{r, hs-print-privu, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_privu.RDS') %>% head(n=20)

knitr::kable(
  df %>% select(-name,-closeness), caption = 'most central private high schools, private colleges and universities') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r, hs-table-privu-agg, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_agg_privu.RDS')

knitr::kable(df, caption = 'characteristics of high schools by degree band, private colleges and universities') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

<!-- public research universities -->

```{r, ego-table-pubu, echo = FALSE}
df <- readRDS('./assets/tables/table_ego_pubu.RDS')
knitr::kable(
  df %>% select(-ID,-Characteristics), row.names = F, # select(-ID, -Characteristics)
  caption = 'ego table caption public universities') %>% landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r, hs-print-pubu, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_pubu.RDS') %>% head(n=20)

knitr::kable(
  df %>% select(-name,-closeness), caption = 'most central private high schools, private colleges and universities') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r, hs-table-pubu-agg, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_agg_pubu.RDS')

knitr::kable(df, caption = 'characteristics of high schools by degree band, private colleges and universities') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

<!-- public and private col/univ -->

```{r, hs-print-both, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_both.RDS') %>% head(n=20)

knitr::kable(
  df %>% select(-name,-closeness), caption = 'most central private high schools, public and private colleges and universities') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r, hs-table-both-agg, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_agg_both.RDS')

knitr::kable(df, caption = 'characteristics of high schools by degree band, public and private colleges and universities') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

@@

```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
knitr::include_graphics('assets/figures/plot_2mode_privu.pdf')
```

@@

```{r emory-region, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Ego network of Emory University, with geographic region"}
knitr::include_graphics('assets/figures/emory_region.pdf')
```

```{r rank-cluster1, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Academic rating of private high schools visited by selected colleges from cluster 1"}
knitr::include_graphics('assets/figures/rank_cluster1.pdf')
```

```{r race-cluster4, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Racial composition of visited private high schools, selected colleges"}
knitr::include_graphics('assets/figures/race_cluster4.pdf')
```

```{r two-mode-plot-pubu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
knitr::include_graphics('assets/figures/plot_2mode_pubu.pdf')
```

```{r two-mode-plot-community, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
knitr::include_graphics('assets/figures/plot_2mode.pdf')
#https://stackoverflow.com/questions/15625990/how-to-set-size-for-local-image-using-knitr-for-markdown
```
